### 2022-02-28 doc/src/MSLevel.tex
Add counter overflow interrupt from extension Sscofpmf

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|c|l|l|}
\hline
Default        &                         & \\
priority order & Major interrupt numbers & \multicolumn{1}{c|}{Description} \\
\hline
\hline
Highest & 63, 62, 31, 30, 61, 60, & Even numbers are standard local
                                     interrupts \\
        & 59, 58, 29, 28, 57, 56, & \ or reserved; odd numbers are
                                     designated \\
        & 55, 54, 27, 26, 53, 52, & \ for custom use \\
        & 51, 50, 25, 24, 49, 48  & \\
\cline{2-3}
        & 11, 3, 7   & Machine interrupts:  external, software, timer \\
        & \ 9, 1, 5  & Supervisor interrupts:  external, software, timer \\
        & 12         & Supervisor guest external interrupt \\
        & 10, 2, 6   & VS interrupts:  external, software, timer \\
\cline{2-3}
        & 47, 46, 23, 22, 45, 44, & Even numbers are standard local
                                     interrupts \\
        & 43, 42, 21, 20, 41, 40, & \ or reserved; odd numbers are
                                     designated \\
        & 39, 38, 19, 18, 37, 36, & \ for custom use \\
Lowest  & 35, 34, 17, 16, 33, 32  & \\
\hline
\end{tabular}
\end{center}
\caption{%
The default priority order for major interrupts 0--63.
Interrupt~63 has the highest default priority, and interrupt~32 has the
lowest default priority.%
}
\label{tab:defaultIntrPrios}
\end{table*}

@@

The local interrupts currently defined by the Advanced Interrupt
Architecture are listed here, in order of decreasing default
priority:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
30 & Reserved for standard reporting of bus or system errors \\
58 & Tentatively reserved for per-core high-power/over-temperature events \\
54 & Reserved for standard high-priority RAS events \\
\noalign{\bigskip}
38 & Reserved for standard low-priority RAS events \\
18 & Debug/trace interrupt \\
\end{displayLinesTable}
\emph{RAS} is an abbreviation for \emph{Reliability, Availability, and
Serviceability}.

@@

When a hart implements one of the local interrupts defined by the
Advanced Interrupt Architecture (an even interrupt number in the
range 16--62), the corresponding bit position is writable in both
\z{mip}/\z{miph} and \z{mie}/\z{mieh}.
An occurrence of the interrupt event causes the interrupt-pending bit
in \z{mip}/\z{miph} to be set to one.
This bit then remains set until cleared by software.

@@

If a local interrupt defined by the Advanced Interrupt Architecture
becomes pending (=~1) in \z{sip}/\z{siph}, the bit in \z{sip}/\z{siph}
is writable and will remain set until cleared by software.

>>>>

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|c|l|l|}
\hline
Default        &                         & \\
priority order & Major interrupt numbers & \multicolumn{1}{c|}{Description} \\
\hline
\hline
Highest & 63, 62, 31, 30, 61, 60, & Even numbers are standard local
                                     interrupts \\
        & 59, 58, 29, 28, 57, 56, & \ or reserved; odd numbers are
                                     designated \\
        & 55, 54, 27, 26, 53, 52, & \ for custom use \\
        & 51, 50, 25, 24, 49, 48  & \\
\cline{2-3}
        & 11, 3, 7   & Machine interrupts:  external, software, timer \\
        & \ 9, 1, 5  & Supervisor interrupts:  external, software, timer \\
        & 12         & Supervisor guest external interrupt \\
        & 10, 2, 6   & VS interrupts:  external, software, timer \\
        & 13         & Counter overflow interrupt \\
\cline{2-3}
        & 47, 46, 23, 22, 45, 44, & Even numbers are standard local
                                     interrupts \\
        & 43, 42, 21, 20, 41, 40, & \ or reserved; odd numbers are
                                     designated \\
        & 39, 38, 19, 18, 37, 36, & \ for custom use \\
Lowest  & 35, 34, 17, 16, 33, 32  & \\
\hline
\end{tabular}
\end{center}
\caption{%
The default priority order for major interrupts 0--63.
Interrupt~63 has the highest default priority, and interrupt~32 has the
lowest default priority.%
}
\label{tab:defaultIntrPrios}
\end{table*}

@@

The {\RISCV} Privileged Architecture currently defines one local
interrupt:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
13 & Counter overflow interrupt\ \ (from extension Sscofpmf) \\
\end{displayLinesTable}
The Advanced Interrupt Architecture defines these additional
local interrupts, listed in order of decreasing default
priority:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
30 & Reserved for standard reporting of bus or system errors \\
58 & Tentatively reserved for per-core high-power/over-temperature events \\
54 & Reserved for standard high-priority RAS events \\
\noalign{\bigskip}
38 & Reserved for standard low-priority RAS events \\
18 & Debug/trace interrupt \\
\end{displayLinesTable}
\emph{RAS} is an abbreviation for \emph{Reliability, Availability, and
Serviceability}.

@@

When a hart implements one of the standard local interrupts defined by
the {\RISCV} Privileged Architecture (number 13, 14, or 15) or by the
Advanced Interrupt Architecture (an even interrupt number in the
range 16--62), the corresponding bit position is writable in both
\z{mip}/\z{miph} and \z{mie}/\z{mieh}.
An occurrence of the interrupt event causes the interrupt-pending bit
in \z{mip}/\z{miph} to be set to one.
This bit then remains set until cleared by software.

@@

If a standard local interrupt
becomes pending (=~1) in \z{sip}/\z{siph}, the bit in \z{sip}/\z{siph}
is writable and will remain set until cleared by software.

### 2022-02-28 doc/src/VSLevel.tex
Add counter overflow interrupt from extension Sscofpmf

Instead of a physical VS-level \z{iprio} array, a separate hardware
mechanism is provided for configuring the priorities of a subset
of interrupts for VS level, using hypervisor CSRs \z{hviprio1} and
\z{hviprio2}, plus, for RV32, their high-half partners, \z{hviprio1h}
and \z{hviprio2h}.
The subset of major interrupt numbers whose priority may be configured
in hardware are these:
\begin{displayLinesTable}[r@{\quad}l]
 1 & Supervisor software interrupt \\
 5 & Supervisor timer interrupt \\
13 & (Reserved interrupt) \\
14 & \quad '' \\
15 & \quad '' \\
16 & \quad '' \\
18 & Debug/trace interrupt \\
20 & (Reserved interrupt) \\
22 & \quad '' \\
24 & \quad '' \\
26 & \quad '' \\
28 & \quad '' \\
30 & (Reserved for standard reporting of bus or system errors) \\
\end{displayLinesTable}
For interrupts directed to VS level, software-configurable priorities
are not supported in hardware for custom interrupts or for any
interrupt numbers higher than~30.

@@

RV32 \z{hviprio1}:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Reserved for priority number for interrupt 0; reads as zero \\
bits 15:8  & Priority number for interrupt 1, supervisor software interrupt \\
bits 23:16 & Reserved for priority number for interrupt 4; reads as zero \\
bits 31:24 & Priority number for interrupt 5, supervisor timer interrupt \\
\end{displayLinesTable}
RV32 \z{hviprio1h}:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Reserved for priority number for interrupt 8; reads as zero \\
bits 15:8  & Priority number for interrupt 13 \\
bits 23:16 & Priority number for interrupt 14 \\
bits 31:24 & Priority number for interrupt 15 \\
\end{displayLinesTable}
RV32 \z{hviprio2}:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Priority number for interrupt 16 \\
bits 15:8  & Priority number for interrupt 18, debug/trace interrupt \\
bits 23:16 & Priority number for interrupt 20 \\
bits 31:24 & Priority number for interrupt 22 \\
\end{displayLinesTable}
RV32 \z{hviprio2h}:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Priority number for interrupt 24 \\
bits 15:8  & Priority number for interrupt 26 \\
bits 23:16 & Priority number for interrupt 28 \\
bits 31:24 & Priority number for interrupt 30 \\
\end{displayLinesTable}

@@

RV64 \z{hviprio1}:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Reserved for priority number for interrupt 0; reads as zero \\
bits 15:8  & Priority number for interrupt 1, supervisor software interrupt \\
bits 23:16 & Reserved for priority number for interrupt 4; reads as zero \\
bits 31:24 & Priority number for interrupt 5, supervisor timer interrupt \\
bits 39:32 & Reserved for priority number for interrupt 8; reads as zero \\
bits 47:40 & Priority number for interrupt 13 \\
bits 55:48 & Priority number for interrupt 14 \\
bits 63:56 & Priority number for interrupt 15 \\
\end{displayLinesTable}
RV64 \z{hviprio2}:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Priority number for interrupt 16 \\
bits 15:8  & Priority number for interrupt 18, debug/trace interrupt \\
bits 23:16 & Priority number for interrupt 20 \\
bits 31:24 & Priority number for interrupt 22 \\
bits 39:32 & Priority number for interrupt 24 \\
bits 47:40 & Priority number for interrupt 26 \\
bits 55:48 & Priority number for interrupt 28 \\
bits 63:56 & Priority number for interrupt 30 \\
\end{displayLinesTable}

>>>>

Instead of a physical VS-level \z{iprio} array, a separate hardware
mechanism is provided for configuring the priorities of a subset
of interrupts for VS level, using hypervisor CSRs \z{hviprio1} and
\z{hviprio2}, plus, for RV32, their high-half partners, \z{hviprio1h}
and \z{hviprio2h}.
The subset of major interrupt numbers whose priority may be configured
in hardware are these:
\begin{displayLinesTable}[r@{\quad}l]
 1 & Supervisor software interrupt \\
 5 & Supervisor timer interrupt \\
13 & Counter overflow interrupt \\
14 & (Reserved interrupt) \\
15 & \quad '' \\
16 & \quad '' \\
18 & Debug/trace interrupt \\
20 & (Reserved interrupt) \\
22 & \quad '' \\
24 & \quad '' \\
26 & \quad '' \\
28 & \quad '' \\
30 & (Reserved for standard reporting of bus or system errors) \\
\end{displayLinesTable}
For interrupts directed to VS level, software-configurable priorities
are not supported in hardware for custom interrupts or for any
interrupt numbers higher than~30.

@@

RV32 \z{hviprio1}:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Reserved for priority number for interrupt 0; reads as zero \\
bits 15:8  & Priority number for interrupt 1, supervisor software interrupt \\
bits 23:16 & Reserved for priority number for interrupt 4; reads as zero \\
bits 31:24 & Priority number for interrupt 5, supervisor timer interrupt \\
\end{displayLinesTable}
RV32 \z{hviprio1h}:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Reserved for priority number for interrupt 8; reads as zero \\
bits 15:8  & Priority number for interrupt 13, counter overflow interrupt \\
bits 23:16 & Priority number for interrupt 14 \\
bits 31:24 & Priority number for interrupt 15 \\
\end{displayLinesTable}
RV32 \z{hviprio2}:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Priority number for interrupt 16 \\
bits 15:8  & Priority number for interrupt 18, debug/trace interrupt \\
bits 23:16 & Priority number for interrupt 20 \\
bits 31:24 & Priority number for interrupt 22 \\
\end{displayLinesTable}
RV32 \z{hviprio2h}:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Priority number for interrupt 24 \\
bits 15:8  & Priority number for interrupt 26 \\
bits 23:16 & Priority number for interrupt 28 \\
bits 31:24 & Priority number for interrupt 30 \\
\end{displayLinesTable}

@@

RV64 \z{hviprio1}:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Reserved for priority number for interrupt 0; reads as zero \\
bits 15:8  & Priority number for interrupt 1, supervisor software interrupt \\
bits 23:16 & Reserved for priority number for interrupt 4; reads as zero \\
bits 31:24 & Priority number for interrupt 5, supervisor timer interrupt \\
bits 39:32 & Reserved for priority number for interrupt 8; reads as zero \\
bits 47:40 & Priority number for interrupt 13, counter overflow interrupt \\
bits 55:48 & Priority number for interrupt 14 \\
bits 63:56 & Priority number for interrupt 15 \\
\end{displayLinesTable}
RV64 \z{hviprio2}:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Priority number for interrupt 16 \\
bits 15:8  & Priority number for interrupt 18, debug/trace interrupt \\
bits 23:16 & Priority number for interrupt 20 \\
bits 31:24 & Priority number for interrupt 22 \\
bits 39:32 & Priority number for interrupt 24 \\
bits 47:40 & Priority number for interrupt 26 \\
bits 55:48 & Priority number for interrupt 28 \\
bits 63:56 & Priority number for interrupt 30 \\
\end{displayLinesTable}
